% Chapter Template

\chapter{Implementation}\doublespacing % Main chapter title

\label{Chapter6} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Chapter VI. \emph{Implementation}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

% ----------------------------
% Introduction
% ----------------------------
\section{Introduction}
During the implementation phase, we, as a team, focused on translating the design and requirements into a functional and robust system. This phase involved the actual development and deployment of the supply chain management solution using blockchain technology. We encountered various challenges along the way, but through collaboration and perseverance, we were able to overcome them and achieve successful results.
\par One of the key aspects of the implementation was the adoption of a microservice architecture using Docker. This allowed us to modularize the system and deploy different components in separate Docker containers. By leveraging Docker, we ensured scalability, flexibility, and portability of our solution. Each organization in the network, including peers and orderers, was hosted within its own Docker container, providing an isolated and consistent environment for running the Hyperledger Fabric nodes.
\par The Hyperledger Fabric framework served as the foundation for our blockchain implementation. It provided us with the necessary tools and protocols for building a secure and decentralized supply chain management system. By leveraging the features of Hyperledger Fabric, such as smart contracts and consensus mechanisms, we were able to create a transparent and tamper-proof ledger for tracking and verifying supply chain transactions.


% ----------------------------
% Brief outline of the study
% ----------------------------

\section{ Experimental Setup}
% \lipsum[22-25]

\subsection{Blockchain Network Setup}
% \lipsum[22-25]
\noindent In the initial step, we will set up the network infrastructure by installing and configuring the necessary dependencies such as Hyperledger Fabric, Docker, and Node.js. Then, we'll establish the network topology, consisting of three organizations (Org1, Org2, and Org3) and a single orderer node. Each organization will have its own cryptographic material generated using the Fabric CA, ensuring secure communication and authentication. 
\subsection{Channel configuration}
% \lipsum[22-25]
\noindent Next, we configured the channel, which involves defining the channel structure and membership. The channel acts as a private communication pathway between the organizations, providing confidentiality and restricted access to transactions and data. We utilize the configtxgen tool to generate the required channel artifacts, including the genesis block. This block serves as the starting point for the channel and contains the initial configuration information.

\subsection{Chaincode Development}
\noindent In this project, we developed a smart 
contract using the Fabric Contract API package and the Node.js SDK in Hyperledger Fabric. By leveraging the Fabric Contract API and Node.js SDK, we can simplify the contract development process and interact with the blockchain network seamlessly. In this section, we will define the contract logic, handle transactions, manage the ledger state, and interact with other network participants. The combination of the Fabric Contract API and Node.js SDK empowers us to build efficient and scalable smart contracts for decentralized applications.
\subsubsection{User Registration}
\input{Chapters/Chapter_6/code/register}
\subsubsection{User Signin}
\input{Chapters/Chapter_6/code/signin}
\subsubsection{create product}
\input{Chapters/Chapter_6/code/createproduct}
\subsubsection{product listing}
\input{Chapters/Chapter_6/code/productlisting}
\subsubsection{send to exporter}
\input{Chapters/Chapter_6/code/sendtoexporter}
\subsubsection{invoice creation}
\input{Chapters/Chapter_6/code/invoicecreation}
\subsubsection{query}
\input{Chapters/Chapter_6/code/query}
\subsection{Machine Learning Model}
\noindent The developed solution presents a machine learning (ML) model for detecting the freshness of fruits using a ConvolutionalNeural Network (CNN) algorithm.The pseuodocode for our model is shown below \par
\begin{lstlisting}[language=Python , caption=ML model]
Mount Drive with Colab
Set Kaggle configuration and download dataset
Unzip the dataset
Access dataset in Drive and copy it to Colab
Prepare the data directories
Display sample images from the dataset
Preprocess the data using ImageDataGenerator
Build the model architecture
Compile the model with optimizer and loss function
Train the model on the training data
Evaluate the model's accuracy and loss
Run the model on uploaded images to make predictions
Save the trained model in different formats
Clean up the kernel
\end{lstlisting}
\noindent Then we use react component to create a page for image classification. It uses the TensorFlow.js library to load and run a the saved model for image classification. The component allows the user to classify images either from the webcam or from a local file. It also provides options to update the model, display predictions, and toggle the webcam.
\noindent 
%\lipsum[22-25]








